Evaluation of probabilistic photometric redshift estimation approaches for \boldblue{ \textsc{The Rubin Observatory Legacy Survey of Space and Time} (LSST)}

### 2020-03-08 paper/tex/appendix.tex
fix LSST naming and typo in appendix
add sentences on potential bias causes

Figure~\ref{fig:pz_pointestimates} shows both point estimates for all codes  both $z_{PEAK}$ and $z_{WEIGHT}$.
Point density is shown with mixed contours to emphasize that most of the galaxies do fall close to the $z_{phot} = z_{spec}$ line, while points trace the details of the catastrophic outlier populations.

@@

The finite grid spacing of the \pzpdf s induces some discretization in $z_{PEAK}$.
The features perpendicular to the $z_{phot} = z_{spec}$ line are due to the $4000$ \AA\ break passing through the gaps between adjacent filters.
Even the strongest codes feature populations far from the $z_{phot} = z_{spec}$ line representing a degeneracy in the space of colours and redshifts.

>>>>

Figure~\ref{fig:pz_pointestimates} shows \sout{both} point estimates \sout{both} $z_{PEAK}$ and $z_{WEIGHT}$ \boldblue{versus true redshift for all codes}.
Point density is shown with mixed contours to emphasize that most of the galaxies do fall close to the $z_{phot} = z_{spec}$ line, while points trace the details of the catastrophic outlier populations.

@@

The finite grid spacing of the \pzpdf s induces some discretization in $z_{PEAK}$.
The features perpendicular to the $z_{phot} = z_{spec}$ line are due to the $4000$ \AA\ break passing through the gaps between adjacent filters.  \boldblue{In the presence of genuine ambiguities in the colour space to redshift mapping, the compression of information down to a single number that is the point estimate redshift fails to adequately capture the more complex nature of the multimodal redshift matching: using the mode selects the highest peak while ignoring posterior probability in lower valued redshift peaks, while measuring the mean of a multimodal PDF often results in a value lying at a redshift between the peaks, removed from either/any of the most likely redshift solutions.  Thus,} \sout{E}even the strongest codes feature populations far from the $z_{phot} = z_{spec}$ line representing a \boldblue{genuine} degeneracy in the space of colours and redshifts.

### 2020-03-08 paper/tex/results.tex
add sentences on potential bias causes

The histogram of PIT values, QQ plot, and QQ difference plot relative to the ideal diagonal are provided in Figure~\ref{fig:pitqq}, showcasing the biases and trends in the average accuracy of the \pzpdf s for each code.
The high QQ values (i.~e.~ more high than low PIT values) of \bpz, \cmnn, \delight, \eazy, and \gpz\ indicate \pzpdf s biased low, and the low QQ values (more low than high PIT values) of \skynet\ and \tpz\ indicate \pzpdf s biased high.
The gray shaded band marks the $2\sigma$ variance in PIT values found using the \trainz\ algorithm with a bootstrap resampling of the training set and a sample size of 30,000 galaxies, representing a very conservative estimate of the representative training sample size estimated as being required for direct \pz\ calibration \citep{Newman:2015}, and thus an approximate minimal error significance compared to ideal performance.
The existence of deviations in the PIT histograms outside of this gray shaded uncertainty range show that significant biases are present for some codes.

@@

The PIT histograms of \delight, \cmnn, \skynet, and \tpz\ feature an underrepresentation of extreme values, indicative of overly broad \pzpdf s, while the overrepresentation of extreme values for \metaphor\ indicates overly narrow \pzpdf s.
These five codes in particular have a free parameter for bandwidth, which may be responsible for this vulnerability, in spite of the opportunity for fine-tuning with perfect prior information.
\flexzboost's ``sharpening'' parameter (described in Section~\ref{sec:flexzboost}) played a key role in diagonalizing the QQ plot, indicating a common avenue for improvement in the approaches that share this type of parameter.
On the other hand, the three purely template-based codes, \bpz, \eazy, and \lephare, do not exhibit much systematic broadening or narrowing, which may indicate that complete template coverage effectively defends from these effects.

>>>>

The histogram of PIT values, QQ plot, and QQ difference plot relative to the ideal diagonal are provided in Figure~\ref{fig:pitqq}, showcasing the biases and trends in the average accuracy of the \pzpdf s for each code.
The high QQ values (i.~e.~ more high than low PIT values) of \bpz, \cmnn, \delight, \eazy, and \gpz\ indicate \pzpdf s biased low, and the low QQ values (more low than high PIT values) of \skynet\ and \tpz\ indicate \pzpdf s biased high.  \boldblue{All three template-based codes use a parameterized functional form for the prior, and deviations from this form in the test set could account for some of the biases seen.  In addition, the \eazy\ and \lephare\ codes both seem to contain an error in how the marginalize over likelihoods, which likely contributes to their observed biases.  For machine learning codes, \delight\ employed a uniform prior in both apparent magnitude and SED type, which could have biased the resultant PDFs, and \gpz\ parameterized all PDFs as a single Gaussian, which may not have been a flexible enough parameterization to capture the full complexity of the posteriors.  In other cases, an obvious source for bias was not discovered, though we note in the particular instance of \tpz\,the results showed a tradeoff in bias versus smoothing width during validation, and a smoothing value that balanced the two effects was chosen.}

The gray shaded band marks the $2\sigma$ variance in PIT values found using the \trainz\ algorithm with a bootstrap resampling of the training set and a sample size of 30,000 galaxies, representing a very conservative estimate of the representative training sample size estimated as being required for direct \pz\ calibration \citep{Newman:2015}, and thus an approximate minimal error significance compared to ideal performance.
The existence of deviations in the PIT histograms outside of this gray shaded uncertainty range show that significant biases are present for some codes.

@@

The PIT histograms of \delight, \cmnn, \skynet, and \tpz\ feature an underrepresentation of extreme values, indicative of overly broad \pzpdf s, while the overrepresentation of extreme values for \metaphor\ indicates overly narrow \pzpdf s.
These five codes in particular have a free parameter for bandwidth, which may be responsible for this vulnerability, in spite of the opportunity for fine-tuning with perfect prior information.  \boldblue{In many cases this bandwidth parameter can be thought of as tuning the size of the neighbourhood of influence in the parameter space of the training data.  Choosing too small of a bandwidth can lead to overfitting and overconfidence, leading to narrow PDFs, while choosing too large of a neighbourhood can oversmooth and lead to overly broad PDFs.} 
\flexzboost's ``sharpening'' parameter (described in Section~\ref{sec:flexzboost}) played a key role in diagonalizing the QQ plot, indicating a common avenue for improvement in the approaches that share this type of parameter.
On the other hand, the three purely template-based codes, \bpz, \eazy, and \lephare, do not exhibit much systematic broadening or narrowing, which may indicate that complete template coverage effectively defends from these effects.
